The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-02 Writeup/paper_v2(merged).tex
reGaussianization included

\begin{keywords}
 Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?} \arun{Yes.}
\end{keywords}

\rachel{Overall comment: the figures need a {\em lot} of work.  First,
  they should be in the same order as they are referenced in the
  text.  Second, they need to be sensibly referenced in the text; you
  can't say ``as we see\dots'' without having a clear statement that
  we should be looking at Fig.~4 (or whatever).  In all
  cases, the font size is way too small, so you should enlarge it.
  The rule of thumb for MNRAS and other journals is that the font size
  in the figures should appear the same size as the font in the text
  of the paper.  (This is true for axis labels, tick labels, and text
  in the legend.)  You also need to write good captions, because some
  people will not really read the paper, just the captions.  MNRAS
  does not use the subfigure environment, so you should remove it.
  Just have the figures on top of or next to each other, and then in
  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever
\section{Introduction}
\label{S:intro}

\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.  I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
Major surveys such as the Dark Energy Survey (DES) are planned to be carried out over the next decade or two to make measurements that constrain the nature of dark energy.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

%The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
In this paper, we show that these large scale structure effects mentioned are indeed present in the data. The rest of the paper is structured as follows.
In \S\ref{sub:overdensities}, we explain how we identify overdensities and underdensities, volume-limit our data in \S\ref{sub:volumelimiting} and in \S\ref{sub:axisratio},
 we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in \S\ref{S:results} and end with conclusions in \S\ref{S:conclusion}.
\section{Data}
\label{S:data}
%In this analysis, we consider the COSMOS sample of galaxies. 
COSMOS~\citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
in the Hubble Space Telescope (HST). Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
is $0.12''$. High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in \cite{SHERA}.
Parametric models to most of these galaxies including \sersicn profile fits, 
2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \cite{Claire_Fits}. This is described briefly in Sec.~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .

Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e. F814W $\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. \rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

@@

 \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
                                       {\bf copied from Mandelbaum 2011.}
\end{enumerate}
\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}

We will analyze how the galaxy morphology and intrinsic shape depends on
the environment in which they reside.

\section{Methods}
\label{S:methods}

@@

Weak lensing simulations will use galaxies selected in 2D redshift slices and
we split our sample in a similar way to assign overdensities.
\rachel{You need a clear and unambiguous statement here as to whether
  or not you are using flux-limited or volume-limited samples.  If the
  latter, then the section on volume-limiting needs to come {\em
    before} this one!  As is, you definitely refer to volume-limiting
  later in this subsection, so the volume-limiting subsection has to
  go first.}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-Squared and the functional form given in~\cite{Redshift_modelling} fits to the histograms.
\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
\rachel{Were you going to use other fitting functions as a test of the
  method?  If so, you should introduce them here.}

The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
{\bf Fig 3 - Histogram with fits }. \\
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  \label{fig:redshift_fluxlimited}
  \caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
\end{figure}

Overdensity in a redshift bin is defined as the ratio of the
difference between the value given by the histogram and the value
predicted by the model to the latter:
$\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.  (\rachel{This $\delta$
  definition is important, so it should be in an equation environment.})
We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.

@@

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} on the zCOSMOS field using spectra and 3D density field reconstruction , except for the last two high redshift bins.
We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
is observed by us in $z=0.80-0.85$ slice.
\rachel{Say why you are doing this comparison with Kovac et al.}

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}
Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
\begin{figure}
 \centering
 a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
 b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
 \label{fig:volume_limiting_dist}
 \caption{ ... }
\end{figure}

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
\rachel{We discussed this in our meeting, so I think you can fix this.}
As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.

\begin{figure*}
 \centering
 \includegraphics[width=0.66\columnwidth]{SMF1} \
 \includegraphics[width=0.66\columnwidth]{SMF2} \
 \includegraphics[width=0.66\columnwidth]{SMF3}
 \caption{SMF plots \rachel{Legend labels need to be better, e.g., $M_I<25.2$.}}
 \label{fig:smf}
\end{figure*}

There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
enough blank space) intersects with the edge of the CCD.
If all galaxies were the same size, this would be a purely random
effect, but in fact bigger galaxies are more likely to get excluded by
this cut. Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts. 
Thus, we use the full F814W$\le$23.5 sample, irrespective of the
existence of postage stamps, and believe that our conclusions are not
affected by this bias. \rachel{What do you mean we use the full sample
  $<23.5$?  For what purpose?  We obviously don't use it for the fits
  or shape estimates, so be specific.}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  \label{fig:redshift_fluxlimited}
  \caption{\rachel{Why does this figure appear again?}}
\end{figure}

@@

\rachel{Tables need to be in a table environment, with a caption.
  Also, you should include the uncategorized slices in here.}
\begin{tabular}{c|c|c|}
 \hline
 Redshift & \# of galaxies & Environment \\
 \hline
 0.30-0.35 & 726 & Overdense \\
 0.35-0.40 & 1000 & Overdense \\
 0.55-0.60 & 727 & Underdense \\
 0.60-0.65 & 1070 & Underdense \\
 0.65-0.70 & 2089 & Overdense \\
 0.70-0.75 & 1970 & Overdense \\
 0.75-0.80 & 1159 & Underdense \\
 0.80-0.85 & 2428 & Overdense \\
 \hline
\end{tabular}

@@

%\section{Implications/Comparisons}
%\section{Results}
\subsection{Describing galaxy morphology and shape}
\label{sub:axisratio}

\rachel{As we discussed, you should get rid of the early parts of this
  regarding second moments, and replace it with a brief description of
  what shape estimates we use from GalSim (re-Gaussianization).}

{\bf Should explain in brief Claire's work.} \\
If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
the boundary may not be well defined and the shape may not be well approximated by an ellipse. Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
we can define the tensor of second brightness moments as
\begin{equation}
 Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
\end{equation}
where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
\begin{align}
 \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
\end{align}
If the image has elliptical isophotes with axis ratio $q$, then 
\begin{equation}
 |\chi| = \frac{1-q^2}{1+q^2}, \;\;\; |\epsilon| = \frac{1-q}{1+q}. 
\end{equation}

@@

\rachel{This section must end with a clear list of the quantities we
  are using from Claire's fits, and from the re-Gaussianization shear
  estimation routine.}

\section{Results}
\label{S:results}
\rachel{Give a big picture summary of the goal of this section.  You
  are taking the results from the previous section and doing what with
  them, and why?}

\rachel{What is entirely missing from this section is the systematic presentation that we discussed in meetings and via e-mail, with clear statements about how the samples have been volume-limited and selected (i.e., luminosity without evolution, with $B$-band evolution, or stellar mass selection)!  That was a critical part of the plan - where did it go?}

The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.

We first compare the distribution of the axis ratio in \emph{all}
overdense bins and \emph{all} underdense bins. The p-value from both
the KS and AD tests are below 0.05 (\rachel{give the actual numbers!}), 
so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level (\rachel{this is a super important result - show the figure!}).
Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
where we expect the distributions to differ.
Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.

>>>>

\begin{keywords}
 Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?}
\end{keywords}

\rachel{The title is overly vague.  I recommend something like ``The
  impact of cosmic variance on simulating weak lensing surveys''.}

\rachel{Also, a question: we had given up on using \sersicn{} or \btt{}
  because the distributions have a complicated form including edge
  effects, but did you ever try looking at a simple statistic like the
  mean value?  i.e., just like your plots of the RMS ellipticity
  vs. redshift with different color points for over/underdense
  regions, except that you would plot $\langle n_s \rangle$ or
  $\langle B/T\rangle$.}

\rachel{Finally, it seems that some of your figure files have not been
  committed to the repository, because I do not see them.  Also I
  cannot compile everything, because the figures are a mix of PDF, PNG, and EPS.
I need either EPS to compile using latex, or PDF and PNG to compile
using pdflatex.}

\section{Introduction}
\label{S:intro}

\rachel{It's true that you should stress the importance of WL.  But
  I recommend restructuring this opening to be {\em constructive}
  rather than the current tone which is relatively negative.  To make
  it constructive, I suggest covering the following points in the
  following order:}
\begin{itemize}
\item Major surveys are planned in the next 1-2 decades
  to make measurements that will precisely constrain the nature of
  dark energy.
\item Weak lensing is one of the more important cosmological probes
  for this purpose.
\item For these upcoming surveys to achieve their promise, the
  systematic error budget must be below the statistical error budget.
  This means reducing systematic errors from their current typical
  level.
\item One method that is commonly used to test for the presence of
  systematics is image simulation.  Typically the most realistic ones
  use HST-based training samples based on COSMOS or the UDF, which are
  small areas of the sky.
\item THe goal of this work is to understand systematic uncertainties
  that might arise due to the finite size of these areas, when
  dividing the sample into redshift slices to test for shear
  systematics as a function of redshift.
\end{itemize}

\rachel{And then you can launch into some of your current text about why there
is cause for concern (known environment-morphology relations, etc.).}
\arun{Done.}

Major surveys such as the Dark Energy Survey (DES) are planned to be carried out over the next decade or two to make measurements that constrain the nature of dark energy.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

%The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
In this paper, we show that these large scale structure effects mentioned are indeed present in the data. The rest of the paper is structured as follows.
In \S\ref{sub:overdensities}, we explain how we identify overdensities and underdensities, volume-limit our data in \S\ref{sub:volumelimiting} and in \S\ref{sub:axisratio},
 we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in \S\ref{S:results} and end with conclusions in \S\ref{S:conclusion}.
\section{Data}
\label{S:data}
%In this analysis, we consider the COSMOS sample of galaxies. 
COSMOS~\citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
in the Hubble Space Telescope (HST). Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
is $0.12''$. High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in ~\cite{SHERA}.
Parametric models to most of these galaxies including \sersicn profile fits, 
2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \S\cite{Claire_Fits}. This is described briefly in~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
\rachel{Technically speaking, \cite{Claire_Fits} did {\em not} fit
  models to these data.  Claire fit models to these data using the
  methodology of \cite{Claire_Fits}, and the appropriate reference
  describing these specific fits is the GREAT3 handbook.  However,
  given that you use them, you do need to say a bit more about them
  then you have already done.  State clearly what models were fit,
  with what free parameters. Finally, be clear about which sample you
  are using.  The SHERA paper only went to 22.5, and the GREAT3
  challenge used galaxies to 23.5.  Since you're using the latter
  sample, you should be very clear about it; currently it seems
  ambiguous. Should also mention the presence of the $I<25.2$ parent
  sample, since you use it quite a bit. (Also, on a more minor note, it is not
  common to call them \sersicn{} profiles, just \sersic{} profiles.)}
\arun{I added GREAT3 reference. More about this is described in \S\ref{sub:axisratio}. Let me know if that's sufficient. The confusion about the sample is now gone, I hope.}

Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e. F814W $\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

@@

 \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
                                       {\bf copied from Mandelbaum 2011.}
\end{enumerate}

We will analyze how these intrinsic shape of the galaxies depends on
the environment in which they reside.

\rachel{If we decide to use stellar masses, then we need to describe
  the stellar mass estimates.}

\arun{Described in the paragraph above}
\section{Methods}
\label{S:methods}

@@

Weak lensing simulations will use galaxies selected in 2D redshift slices and
we split our sample in a similar way to assign overdensities.

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our sample of galaxies, upto $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-Squared and the functional form given in~\cite{Redshift_modelling} fits to the histograms.
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
\rachel{Were you going to use other fitting functions as a test of the
  method?  If so, you should introduce them here.}

The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
{\bf Fig 3 - Histogram with fits }. \\
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  \label{fig:redshift_fluxlimited}
  \caption{}
\end{figure}

Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$. 
We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
\rachel{Let's not discard them.  We should just treat them as
  ``environmentally neutral.''  You do after all show them on your plots.}

@@

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} on the zCOSMOS field using spectra and 3D density field reconstruction , except for the last two high redshift bins.
We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
is observed by us in $z=0.80-0.85$ slice.

@@

\rachel{I think ``arbitrary'' is not the right word ot use in this
  paragraph.  It's obviously well-motivated in a general sense, and
  the question is whether it's robust or not.  Comparison with a more
  robust 3d method is what we use as validation to say that it's
  robust enough for our purposes.}
\arun{Done.}

\subsection{Volume limiting}
\label{sub:volumelimiting}
COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
\begin{figure}
 \centering
 a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
 b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
 \label{fig:volume_limiting_dist}
 \caption{ ... }
\end{figure}

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
We plot their SMF for \emph{all} in ~\ref{fig:smf} for reference. Their SMF is higher than ours since they reach $K_s$-band $5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.

\begin{figure*}
 \centering
 \includegraphics[width=0.66\columnwidth]{SMF1} \
 \includegraphics[width=0.66\columnwidth]{SMF2} \
 \includegraphics[width=0.66\columnwidth]{SMF3}
 \caption{SMF plots}
 \label{fig:smf}
\end{figure*}

There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box. \arun{Rachel, please correct my terminology here.}
While the former is purely random and doesn't introduce bias, the latter is not. Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts. 
Thus, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, and believe that our conclusions are not affected by this bias.

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  \label{fig:redshift_fluxlimited}
  \caption{}
\end{figure}

@@

\begin{tabular}{c|c|c|}
 \hline
 Redshift & \# of galaxies & Environment \\
 \hline
 0.30-0.35 & 726 & Overdense \\
 0.35-0.40 & 1000 & Overdense \\
 0.55-0.60 & 727 & Underdense \\
 0.60-0.65 & 1070 & Underdense \\
 0.65-0.70 & 2089 & Overdense \\
 0.70-0.75 & 1970 & Overdense \\
 0.75-0.80 & 1159 & Underdense \\
 0.80-0.85 & 2428 & Overdense \\
 \hline
\end{tabular}

@@

%\section{Implications/Comparisons}
%\section{Results}
\subsection{Finding fit parameters}
\label{sub:axisratio}
{\bf Should explain in brief Claire's work.} \\
If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
the boundary may not be well defined and the shape may not be well approximated by an ellipse. Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
we can define the tensor of second brightness moments as
\begin{equation}
 Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
\end{equation}
where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
\begin{align}
 \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
\end{align}
If the image has elliptical isophotes with axis ratio $q$, then 
\begin{equation}
 |\chi| = \frac{1-q^2}{1+q^2}, \;\;\; |\epsilon| = \frac{1-q}{1+q}. 
\end{equation}

@@

\section{Results}
\label{S:results}
The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.

We first compare the distribution of the axis ratio in \emph{all} overdense bins and \emph{all} underdense bins. The p-value from both the KS and AD tests are below 0.05, 
so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
where we expect the distributions to differ.
Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
